Mental Health Analysis

### 2020-03-16 05_mental_health.Rmd

```{r access_map}
# this interactive map is much easier to create and explore
pal <- colorBin("GnBu", c(tracts$access_ls, tracts$multi_ls), n = 5)
leaflet(tracts) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(group = "Kinner", color = ~ pal(multi_ls),
              label = ~as.character(round(multi_ls, 2))) %>%
  addLegend(pal = pal, values = ~multi_ls, title = "Access Score")
```

@@

Let's look at some residuals

>>>>

```{r access_map}
# this interactive map is much easier to create and explore
pal <- colorBin("viridis", c(tracts$access_ls, tracts$multi_ls), n = 5)
leaflet(tracts) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(group = "Kinner", color = ~ pal(multi_ls),
              label = ~as.character(round(multi_ls, 2)), 
              stroke = FALSE, fillOpacity = 0.7) %>%
  addLegend(position = "topleft", pal = pal, values = ~multi_ls, title = "Access Score")
```

@@

### Utah Analysis

```{r}
tibble("Age" = c("18-25", "26-49", "50+"), "Serious MI" = c(7.5, 5.6, 2.7),
       "Any MI" = c(25.8, 22.2, 13.8)) %>%
  mutate(`Any MI` = `Any MI` - `Serious MI`) %>%
  gather("Type of Mental Illness", "Percent", -Age) %>%
  ggplot(aes(x = Age, y = Percent, fill = Malady)) +
  geom_bar(stat = "identity")
```

Get 500 cities mental health data for Utah County

```{r}
cdc_urls <- list(
  "mhealth" = "https://chronicdata.cdc.gov/resource/i2ek-k3pa.json?stateabbr=UT"
)

cdc500 <- lapply(cdc_urls, function(url){
  read.socrata(url, app_token = Sys.getenv("CDC_KEY"),
               stringsAsFactors = FALSE) %>%
    tbl_df() %>%
    filter(tractfips %in% acs$geoid) %>%
    transmute( geoid = tractfips, value = as.numeric(data_value ), year = year)
}) %>%
  bind_rows(.id = "measure") 
```

Get block groups
```{r}
bg <- tigris::block_groups("Utah", "Utah", class = "sf") %>%
  mutate(tract = substr(GEOID, 1, 11)) %>%
  left_join(cdc500, by = c("tract" = "geoid"))
```

map

```{r}
pal <- colorNumeric(palette = "magma", bg$value)
leaflet(bg) %>% addProviderTiles(providers$Esri.WorldGrayCanvas) %>% 
  addPolygons(color = ~pal(value))
```
